A Large-Scale Study of the Use of Eval in R

### 2020-08-27 inst/paper/main.tex
reorder

\lstset{ 
 language=R,              % the language of the code
 basicstyle=\small\ttfamily,    % the size of the fonts
% numbers=left,            % where to put the line-numbers
 numberstyle=\color{Blue},% the style that is used for the line-numbers
 stepnumber=1,            % the step between two line-numbers. If it is 1,
                          % each line will be numbered
 numbersep=2pt,           % how far the line-numbers are from the code
 backgroundcolor=\color{white},  % choose the background color.
 showspaces=false,        % show spaces adding particular underscores
 showstringspaces=false,  % underline spaces within strings
 showtabs=false,          % show tabs within strings adding particular 
%frame=single,            % adds a frame around the code
 rulecolor=\color{black}, % if not set, the frame-color may be changed on
                          % line-breaks within not-black text (e.g. commens
                          % (green here))
 tabsize=2,               % sets default tabsize to 2 spaces
 captionpos=b,            % sets the caption-position to bottom
 breaklines=true,         % sets automatic line breaking
 breakatwhitespace=false, % sets if automatic breaks should only happen at 
 keywordstyle=\color{Blue},    % keyword style
 commentstyle=\color{YellowGreen},  % comment style
 stringstyle=\color{ForestGreen}    % string literal style
} 
\begin{document}

@@

\newcommand{\eg}{\emph{e.g.},\xspace}
\newcommand{\ie}{\emph{i.e.},\xspace}
\newcommand{\cf}{\emph{cf.}\xspace}
\newcommand{\summary}[1]{({\csname #1Min\endcsname} / {\csname #1Mean\endcsname} / {\csname #1Max\endcsname})}
\newcommand{\summaryrnd}[1]{({\csname #1MinRnd\endcsname} / {\csname #1MeanRnd\endcsname} / {\csname #1MaxRnd\endcsname})}

@@

We have selected the TOP \CorpusPackages packages based on the number of reverse
dependencies, \ie how many other packages depend on them\footnote{Extracted from
  package metadata using builtin function}. Using this criterion helps us to
choose popular packages which in general should be of a better quality and have
better code coverage and therefore more code to run. The resulting set has
\summary{CorpusRevdeps}\footnote{Such triples represent ($min$ / $mean$ /
  $max$)} reverse dependencies and consists of \CorpusRCodeRnd lines of R code
and \CorpusNativeCodeRnd lines of native code (C/C++/Fortran)\footnote{Excluding
  comments and blank lines using \url{github.com/AlDanial/cloc}}.
Figure~\ref{fig:corpus} shows these packages, the size of the dots reflects the
project's size in lines of code including both R and native code, the x-axis
indicates the expression code coverage in percents and the y-axis gives the
number of reverse dependencies in log scale. Dotted lines indicate means.
Packages with over \CorpusEvalsPackageTreshold eval call sites are annotated.

@@

The selected packages contain \CorpusPackagePrograms programs with
\CorpusPackageProgramsCodeRnd lines of R code:
%
\begin{compactitem}[$-$]
  \item \CorpusExamplesProgramsRnd examples with \CorpusExamplesCodeRnd
  \summaryrnd{CorpusExamplesCode} lines of code,
  \item \CorpusTestsProgramsRnd tests with \CorpusTestsCodeRnd
  \summaryrnd{CorpusTestsCode} lines of code, and
  \item \CorpusVignettesProgramsRnd vignettes with \CorpusVignettesCodeRnd
  \summaryrnd{CorpusVignettesCode} lines of code.
\end{compactitem}

@@

The final set contains \CorpusFinishedKaggle kernels with
\CorpusFinishedKaggleCodeRnd \summaryrnd{CorpusFinishedKaggleCode} lines of R
code.

@@

\begin{table}[ht]
\resizebox{\columnwidth}{!}{%
\begin{tabular}{@{}r|ccc@{}} \hline
Source & Core & Dependent & Own \\\hline
      %      CRAN & \CranCoreTotalEvalCallsRnd (\CranCoreMinEvalCallsRnd/\CranCoreAvgEvalCallsRnd/\CranCoreMaxEvalCallsRnd) & \CranDependentTotalEvalCallsRnd (\CranDependentMinEvalCallsRnd/\CranDependentAvgEvalCallsRnd/\CranDependentMaxEvalCallsRnd) & \CranOwnTotalEvalCallsRnd (\CranOwnMinEvalCallsRnd/\CranOwnAvgEvalCallsRnd/\CranOwnMaxEvalCallsRnd) \\
CRAN & \CranCoreTotalEvalCallsRnd (1 / 581 / 416K)  & \CranDependentTotalEvalCallsRnd (1 / 532 / 183K) & \CranOwnTotalEvalCallsRnd (1 / 292 / 144K)\\
Kaggle & \KaggleCoreTotalEvalCallsRnd (1 / 412 / 2.8K) & \KaggleDependentTotalEvalCallsRnd (3 / 96 / 1.1K) & 0 (0 / 0 / 0) \\
%      Kaggle & \KaggleCoreTotalEvalCallsRnd (\KaggleCoreMinEvalCallsRnd/\KaggleCoreAvgEvalCallsRnd/\KaggleCoreMaxEvalCallsRnd) & \KaggleDependentTotalEvalCallsRnd (\KaggleDependentMinEvalCallsRnd/\KaggleDependentAvgEvalCallsRnd/\KaggleDependentMaxEvalCallsRnd) & 0(0/0/0) \\
      \hline
    \end{tabular}
  }
  \caption{Eval calls in CRAN and Kaggle}
  \label{A}
\end{table}

@@

\begin{table}[ht]\resizebox{\columnwidth}{!}{%
\begin{tabular}{rr|rr|rr}\hline
Callsites & Packages & Callsites & Packages & Callsites & Packages \\ \hline
\SiteSummarySiteCountA & \SiteSummaryPackageCountA & \SiteSummarySiteCountF & \SiteSummaryPackageCountF & \SiteSummarySiteCountK & \SiteSummaryPackageCountK \\
\SiteSummarySiteCountB & \SiteSummaryPackageCountB & \SiteSummarySiteCountG & \SiteSummaryPackageCountG & \SiteSummarySiteCountL & \SiteSummaryPackageCountL \\
\SiteSummarySiteCountC & \SiteSummaryPackageCountC & \SiteSummarySiteCountH & \SiteSummaryPackageCountH & \SiteSummarySiteCountM & \SiteSummaryPackageCountM \\
\SiteSummarySiteCountD & \SiteSummaryPackageCountD & \SiteSummarySiteCountI & \SiteSummaryPackageCountI & \SiteSummarySiteCountN & \SiteSummaryPackageCountN \\
      \SiteSummarySiteCountE & \SiteSummaryPackageCountE & \SiteSummarySiteCountJ & \SiteSummaryPackageCountJ & \SiteSummarySiteCountO & \SiteSummaryPackageCountO \\    \hline
\end{tabular}} \label{table:site-package-summary}
\caption{Distribution of callsites in CRAN}
\end{table}

@@

\section{Side-Effects}

@@

\subsection{Operation mix}

Here we should show some information about what happens during an eval. What kinds of operations...

>>>>

\lstset{ 
 language=R,              % the language of the code
 basicstyle=\small\ttfamily,    % the size of the fonts
% numbers=left,            % where to put the line-numbers
 numberstyle=\color{Blue},% the style that is used for the line-numbers
 stepnumber=1,            % the step between two line-numbers. If it is 1,
                          % each line will be numbered
 numbersep=2pt,           % how far the line-numbers are from the code
 backgroundcolor=\color{white},  % choose the background color.
 showspaces=false,        % show spaces adding particular underscores
 showstringspaces=false,  % underline spaces within strings
 showtabs=false,          % show tabs within strings adding particular 
%frame=single,            % adds a frame around the code
 rulecolor=\color{black}, % if not set, the frame-color may be changed on
                          % line-breaks within not-black text (e.g. commens
                          % (green here))
 tabsize=2,               % sets default tabsize to 2 spaces
 captionpos=b,            % sets the caption-position to bottom
 breaklines=true,         % sets automatic line breaking
 breakatwhitespace=false, % sets if automatic breaks should only happen at 
 keywordstyle=\color{Blue},    % keyword style
 commentstyle=\color{YellowGreen},  % comment style
 stringstyle=\color{ForestGreen}    % string literal style
}

% https://tex.stackexchange.com/questions/351435/table-name-placment-in-tabular-documentclass-ieeetran-conference
\makeatletter
\def\@IEEEtablestring{figure}
\makeatother

\begin{document}

@@

\newcommand{\eg}{\emph{e.g.},\xspace}
\newcommand{\ie}{\emph{i.e.},\xspace}
\newcommand{\cf}{\emph{cf.}\xspace}
\newcommand{\summary}[1]{{\csname #1\endcsname} ({\csname #1Min\endcsname} / {\csname #1Mean\endcsname} / {\csname #1Max\endcsname})}
\newcommand{\summaryrnd}[1]{{\csname #1Rnd\endcsname} ({\csname #1MinRnd\endcsname} / {\csname #1MeanRnd\endcsname} / {\csname #1MaxRnd\endcsname})}

@@

We have selected the TOP \CorpusPackages packages based on the number of reverse
dependencies, \ie how many other packages depend on them\footnote{Extracted from
  package metadata using builtin function}. Using this criterion helps us to
choose popular packages which in general should be of a better quality and have
better code coverage and therefore more code to run. The resulting set contains
\CorpusRCodeRnd lines of R code and \CorpusNativeCodeRnd lines of native code
(C/C++/Fortran)\footnote{Excluding comments and blank lines using
  \url{github.com/AlDanial/cloc}}. Figure~\ref{fig:corpus} shows these packages,
the size of the dots reflects the project's size in lines of code including both
R and native code, the x-axis indicates the expression code coverage in percents
and the y-axis gives the number of reverse dependencies in log scale. Dotted
lines indicate means. Packages with over \CorpusEvalsPackageTreshold eval call
sites are annotated.

@@

The selected packages contain \CorpusPackagePrograms programs with
\CorpusPackageProgramsCodeRnd lines of R code:
%
\begin{compactitem}[$-$]
  \item \CorpusExamplesProgramsRnd examples with
  \summaryrnd{CorpusExamplesCode}\footnote{This notation represents $sum$ ($min$
    / $mean$ / $max$)} lines of code,
  \item \CorpusVignettesProgramsRnd vignettes with
  \summaryrnd{CorpusVignettesCode} lines of code.
\end{compactitem}

@@

The final set contains \CorpusFinishedKaggle kernels with
\summaryrnd{CorpusFinishedKaggleCode} lines of R code.

@@

 \begin{table*}[tb]
   \centering
   \begin{tabular}{r|c|c|c@{}} \hline
     Corpus / Source & Core                              & Dependent                              & Own \\\hline
     CRAN   & \summaryrnd{CranCoreEvalCalls}    & \summaryrnd{CranDependentEvalCalls}    & \summaryrnd{CranOwnEvalCalls} \\
     Kaggle & \summaryrnd{KaggleCoreEvalCalls}  & \summaryrnd{KaggleDependentEvalCalls}  & \summaryrnd{KaggleOwnEvalCalls} \\\hline
   \end{tabular}
   \caption{Eval calls in CRAN and Kaggle}
   \label{A}
 \end{table*}

@@

\begin{table}[ht]\resizebox{\columnwidth}{!}{%
\begin{tabular}{rr|rr|rr}\hline
 Callsites & Packages & Callsites & Packages & Callsites & Packages \\\hline
\input{tag/table-site-package-summary.tex}
\end{tabular}}
\caption{Distribution of callsites in CRAN}
\label{table:site-package-summary}
\end{table}

@@

\subsection{Operation Mix}

Unlike Javascript, R packages also call native code for access to efficient
numerical and statistical routines. We intercept all calls to R functions and
native functions from the programs and \eval calls. In the whole corpus there
are \AllClosureCallCount calls to R functions and \AllNativeCallCount to native
code. Of those, \eval contribute to only \EvalClosureCallCount calls to R
functions and \EvalNativeCallCount to native code.

\subsection{Side-Effects}

@@
